A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Proposal upgrade

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful optimization algorithms have previously found
their inspiration. Our focus was not on a single animal species but all of
them, using general abstraction to identify what those species have in common.
In our analysis, we consider a broad animal spectrum, from bacteria to humans
and lions, finding our inspiration on the biological Life Cycle of the animal
species.

In this paper, we present an algorithm inspired by the biological Life-Cycle of
animal species, which consists of several stages \cite{read1968system}: birth, growth, reproduction,
and death. As in nature, we intend to execute all these stages in parallel and
asynchronously on a population that evolves constantly.

>>>>

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful optimization algorithms have previously found
their inspiration. Our focus was not on a single animal species but all of
them, using general abstraction to identify what those species have in common.

In our analysis, we consider a broad animal spectrum, from bacteria to humans
and lions, finding our inspiration on the biological Life Cycle of the animal
species, which consists of several stages \cite{read1968system}: birth, growth,
reproduction, and death. As in nature, we intend to execute all these stages in
parallel and asynchronously on a population that evolves constantly. The
combination of those processes is what we call evolution.
